Testing Education State Transitions

### 2023-06-16 minos/testing/education_transitions.Rmd
Added some code to save plots in the education_transitions.Rmd testing notebook

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers", 'SIPHER7')
create.if.not.exists(save.path)

shall.we.save <- TRUE
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r}
start.year <- 2020
save.path <- here::here("plots", "education")
create.if.not.exists(save.path)
```

@@

ggsave(filename = 'education_state_0.png',
       path = save.path)

@@

ggsave(filename = 'education_state_1.png',
       path = save.path)

@@

ggsave(filename = 'education_state_2.png',
       path = save.path)

@@

ggsave(filename = 'education_state_3.png',
       path = save.path)

@@

ggsave(filename = 'education_state_5.png',
       path = save.path)

@@

ggsave(filename = 'education_state_6.png',
       path = save.path)

@@

ggsave(filename = 'education_state_7.png',
       path = save.path)

@@

ggsave(filename = 'education_state_overlaid.png',
       path = save.path)

@@

ggsave(filename = 'mean_age_achieved_educ.png',
       path = save.path)
